---
title: "Cross Validation for Logistic Discrimination"
author: "林敬昇、陳昱霈、楊崇甫"
date: "2015年10月15日"
output: html_document
---

# Cross Validation by package glmnet

### Loading glmnet package

```{r}
library(glmnet)
```

### Loading dataset : newfish

載入資料集

```{r}
fish <- read.table('/Users/sheng/Documents/NCCU/ML/NCCU_ML_Note/lab/fish.txt',header=T)
L21<-fish$L2-fish$L1
L32<-fish$L3-fish$L2
L31<-fish$L3-fish$L1
newfish<-cbind(fish,L21,L32,L31)
```

檢視資料集

```{r}
str(newfish)
```

資料整理

```{r}
x <- as.matrix(newfish[,-1])
y <- newfish$Species
```


### Cross Validation

利用cv.glmnet執行CV. 

其中參數設定可以透過`?cv.glmnet`查詢

列出幾項重要參數：

- lambda : 不確定是不是上課老師說的alpha
- nfolds : nfolds can be as large as the sample size `(leave-one-out CV)`
- type.measure : type.measure="class" applies to binomial and multinomial logistic regression only, and gives misclassification error.

參考`?cv.glmnet`標頭`Value`中的Objects, 包含：

- lambda : the values of lambda used in the fits.
- `cvm` : The mean cross-validated error - a vector of length length(lambda).
- `cvsd` : estimate of standard error of cvm.
- cvup : upper curve = cvm+cvsd.
- cvlo :	lower curve = cvm-cvsd.

```{r,warning=F}
cvfit = cv.glmnet(x, y,family='multinomial',
                  nfolds=148, 
                  type.measure='class',
                  parallel = TRUE)
plot(cvfit)
length(cvfit$cvm)
predict.value <- predict(cvfit, x, s = "lambda.min", type = "class")
table(predict.value,newfish$Species)
```

